### 2018-04-18 paper.Rmd
other edits

The data contained in CHILDES is populated from a diverse array of studies that adhered to varying conditions and paradigms.
This point is particularly salient in our gender analysis due to potential non-independence issues that result from longitudinal studies.
For this reason, we fit a linear fixed effects model (`mod_data`, shown in the plot below) to remedy these concerns.^[All code and analyses are available at https://github.com/langcog/childes-db-paper] 
The plot below displays the average MTLD scores for various children at different ages, split by gender, with a line corresponding to our mixed effects model.

<!-- AS: not sure whether I should have included this; I didn't want to overwhelm the reader -->
<!-- SM: need a few more details: what kind of model was it basically? loess, logistic growth curve, etc. -->

@@

This plot reveals a slight gender difference in linguistic productivity in young children (displaying a moderate female advantage), replicating the results of @eriksson2012differences.
The goal of this analysis was to showcase an example of the the steps involved in using `childesr` for exploring the CHILDES dataset, as well as some of the potential hazards in working with a diverse set of corpora, many of which are longitudinal.

>>>>

The data contained in CHILDES is populated from a diverse array of studies that adhered to varying conditions and paradigms.
This point is particularly salient in our gender analysis due to potential non-independence issues that result from longitudinal studies.
For this reason, we fit a linear mixed effects model (`mod_data`, shown in the plot below) to remedy these concerns.^[All code and analyses are available at https://github.com/langcog/childes-db-paper] 
The plot below displays the average MTLD scores for various children at different ages, split by gender, with a line corresponding to our mixed effects model.

<!-- AS: is this sufficient for mixed effects model explanation? -->

@@

This plot reveals a slight gender difference in linguistic productivity in young children (displaying a moderate female advantage), replicating the results of @eriksson2012differences.
The goal of this analysis was to showcase an example of the the steps involved in using `childesr` for exploring the CHILDES dataset, as well as some of the potential hazards in working with a diverse set of corpora that were collectd through various experimental paradigms.
